How to Avoid OOTA Without Really Trying

### 2024-09-10 paper/ootavacuous.tex
Shrink section 8 (Future Directions)
Section 8 can be made considerably shorter by replacing verbose text
with a simple itemized list.

Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

This paper focuses solely on compilers, but it should be possible to
extend these results to some classes of interpreters and JITs on the
one hand and to link-time optimizations (LTO) on the other.

This paper focuses primarily on compilers that do only local per-thread
analysis.
Further explorations could consider additional classes of global analysis,
for example, analyses that demonstrate that a given expression will
always evaluate to a particular constant.
JMM Causality Test Case 1 % %%% Cite P3064.
% %%% discussed in
% %%% Appendix~\ref{app:Causality Test Case 1}
provides an example of such a global analysis.

This paper assumes that the user defines threads, and that the
C++ implementation executes those threads unchanged.
Future analyses might examine the possibility of ``flattening''
optimizations that combine multiple threads into one.
(Note that such optimizations are more difficult than they might first appear.)

This paper shows that semantic dependencies are relative to specific
executions of a program and the specific compiler in use rather than
being determined solely by the source code.
Future work might expand on
Section~\ref{sec:Relative versus Absolute Dependency},
exploring special cases in which absolute semantic dependencies are
functions just of the source code.

This paper considers only programs whose threads
communicate using shared memory.
Future work might include the effects of input and output or
other operations which can vary from one execution to another,
such as those based on the current time, process IDs, or pointer values
(see Section~\ref{sec:Effect of Memory Layout}).

Finally, future work might expand on
Section~\ref{sec:Issues and Refinements}
so as to more precisely delineate the limits of permissible
behavior for quasi-volatile object accesses.

>>>>

This paper focused solely on compilers, primarily those that do only
local per-thread anaylsis and optimization.
It introduced the notion of quasi-volatile object accesses and gave
a definition for semantic dependency that is relative to a particular
C++ implementation.

Further explorations could:
\begin{itemize}
\item	Extend these results to some classes of interpreters and JITs
	on one hand, and to link-time optimizations (LTO) on the other.
\item	Consider various classes of global analysis, such as
	demonstrating that a given expression will always evaluate
	to a constant.
\item	Examine the possibility of ``flattening'' optimizations that
	combine multiple threads into one.
\item	Explore cases in which semantic dependencies must be absolute,
	not relative to any particular compiler.
\item	Include the effects of input and output or other operations
	which can vary from one execution to another.
\item	Delineate more precisely the limits of permissible behavior
	for quasi-volatile object accesses.
\end{itemize}
